Moisture absorption and drying alter nonadditive litter flammability in a mixed conifer forest

### 2020-05-01 ms/Magalhaes_Schwilk_litter_flam_moisture.tex
fixup

\nwords{6330 (main text only), 8000 (abstract, text, captions) }
\ntables{4}
\nfig{5}
\nref{55}

@@

      \item Moisture dynamics varied across species with higher specific leaf
    area being associated with higher maximum absorption and lower litter bulk
    density being associated with faster drying rates. We found that these
    differing moisture dynamics resulted in time since wetting having strongly
    differing effects on flammability across the major litter types typified by
    different tree taxa..

>>>>

\nwords{6330 (main text only), 8000 (abstract, text, captions) }
\ntables{4}
\nfig{5}
\nref{57}

@@

      \item Moisture dynamics varied across species with higher specific leaf
    area being associated with higher maximum absorption and lower litter bulk
    density being associated with faster drying rates. We found that these
    differing moisture dynamics resulted in time since wetting having strongly
    differing effects on flammability across the major litter types typified by
    different tree taxa.
